Declarative Methods Term Project: \\ JumanG

### 2013-05-03 doc/paper.tex
cool beans

\documentclass{article}
\author{Juneki Hong and Michael Tango}
\title{Declarative Methods Term Project: \\ JumanG}
%\usepackage[ampersand]{easylist}

\begin{document}

\maketitle
\newpage

@@

\section{Problem we decided to solve}

\section{How we solved it}

Encoder

Solver

Decoder

@@

@@

\subsection{The Decoder}

\section{The results}

@@

>>>>

\documentclass{article}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Declarative Methods Term Project: \\ JumanG}
\author{Juneki Hong and Michael Tango}

%\usepackage[ampersand]{easylist}

\date{}
\begin{document}
\maketitle

\begin{abstract}
We attempted to display a description of a graph in a nicely formatted 
We approached this problem using a variety of different algorithms
\end{abstract}

@@

\section{Graph Drawing}

\section{Declarative Pipeline}

We had an Encoder, Solver, and a Decoder

@@

\subsubsection{Radial Solver}
Radial displays have been used for some time to display trees of various data in a way different from the typical top-down approach.
Rarely, however, has it been used to display graphs. We implemented a solver that lays out a graph radially, from the center out.
These

@@

\subsection{The Decoder}
Tikz

@@

\section{Conclusions}
